Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-07-04 inst/surfing_jsa.tex
documentation for directlogplotofstrengths_postinkscape.pdf

\begin{figure}[h]
\includegraphics[width=4in]{directlogplotofstrengths_postinkscape.pdf}
\caption{Scatterplot of points scored  \label{compare_likelihood_points}
against maximum likelihood estimates}
\end{figure}

>>>>

\begin{figure}[h]
  \includegraphics[width=4in]{directlogplotofstrengths_postinkscape.pdf}  % to create this file, open directlogplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directlogplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directlogplotofstrengths.pdf, with slight optical glitches removed.  File directelogplotofstrengths.pdf is produced by surfing.Rmd.
\caption{Scatterplot of points scored  \label{compare_likelihood_points}
against maximum likelihood estimates}
\end{figure}
